Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-16 Submission.Rmd
Working on correlation table display issue

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  caption = "Challenge, hindrance, and resource bivariate correlations.",
                  escape = FALSE, 
                  font_size = "tiny",  ## "tiny" smallest
                  longtable = TRUE,
                  landscape = TRUE,
#                  stub_indents = list(a=1:10, b = 11:21),
                  note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
```

>>>>

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
                  caption = "Challenge, hindrance, and resource bivariate correlations.",
                  escape = FALSE, 
                  font_size = "tiny",  ## "tiny" smallest
                  longtable = TRUE,
                  landscape = TRUE,
#                  stub_indents = list(a=1:10, b = 11:21),
                  note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
trial <- data_new[c(405:411, 413:419, 421:427)]
library(apaTables)
apa.cor.table(trial, filename = "cor.doc", show.conf.interval = FALSE, landscape = TRUE)

### 2023-03-16 Submission.tex
Working on correlation table display issue

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} eRg\\\textsuperscript{3} PepsiCo}

@@

>>>>

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin-Stout\\\textsuperscript{2} eRg\\\textsuperscript{3} PepsiCo}

@@

The ability to suppress reporting of reporting confidence intervals has been deprecated in this version.
The function argument show.conf.interval will be removed in a later version.

Means, standard deviations, and correlations with confidence intervals

Variable M SD 1 2 3\\
1. onet.resource.ii 3.98 0.80

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\item
  onet.resource.mp 4.19 0.60 .61**\\
  {[}.55, .66{]}
\item
  onet.resource.wo 3.79 0.84 .46** .50**\\
  {[}.40, .53{]} {[}.43, .56{]}
\item
  onet.resource.io 4.10 0.60 .49** .64** .45**\\
  {[}.42, .55{]} {[}.59, .69{]} {[}.38, .51{]}
\item
  onet.resource.ir 3.80 0.61 .46** .55** .37**\\
  {[}.40, .53{]} {[}.48, .60{]} {[}.30, .44{]}
\item
  onet.resource.pc 2.99 0.77 .19** .15** .32**\\
  {[}.11, .27{]} {[}.07, .23{]} {[}.24, .39{]}
\item
  onet.resource.sc 3.65 0.61 .43** .46** .41**\\
  {[}.36, .50{]} {[}.39, .52{]} {[}.34, .48{]}
\item
  onet.hindrance.ii 2.15 1.01 -.26** -.26** -.17**\\
  {[}-.34, -.18{]} {[}-.34, -.18{]} {[}-.25, -.09{]}
\item
  onet.hindrance.mp 2.10 1.05 -.23** -.30** -.17**\\
  {[}-.31, -.15{]} {[}-.38, -.22{]} {[}-.25, -.09{]}
\item
  onet.hindrance.wo 2.31 1.02 -.21** -.25** -.22**\\
  {[}-.29, -.13{]} {[}-.33, -.17{]} {[}-.30, -.14{]}
\item
  onet.hindrance.io 2.23 1.03 -.22** -.27** -.14**\\
  {[}-.30, -.14{]} {[}-.34, -.19{]} {[}-.22, -.06{]}
\item
  onet.hindrance.ir 2.35 0.89 -.22** -.24** -.15**\\
  {[}-.30, -.14{]} {[}-.32, -.17{]} {[}-.23, -.07{]}
\item
  onet.hindrance.pc 2.66 0.83 -.04 -.08* -.09*\\
  {[}-.12, .05{]} {[}-.17, -.00{]} {[}-.17, -.01{]}
\item
  onet.hindrance.sc 2.64 0.80 -.13** -.15** -.13**\\
  {[}-.22, -.05{]} {[}-.23, -.06{]} {[}-.21, -.04{]}
\item
  onet.challenge.ii 3.98 0.80 .62** .49** .37**\\
  {[}.56, .67{]} {[}.42, .55{]} {[}.30, .44{]}
\item
  onet.challenge.mp 4.20 0.64 .47** .63** .42**\\
  {[}.40, .53{]} {[}.58, .68{]} {[}.35, .49{]}
\item
  onet.challenge.wo 3.65 0.88 .34** .39** .64**\\
  {[}.26, .41{]} {[}.31, .45{]} {[}.58, .68{]}
\item
  onet.challenge.io 4.07 0.64 .34** .48** .33**\\
  {[}.26, .41{]} {[}.41, .54{]} {[}.26, .41{]}
\item
  onet.challenge.ir 3.85 0.63 .32** .40** .26**\\
  {[}.24, .39{]} {[}.33, .47{]} {[}.18, .34{]}
\item
  onet.challenge.pc 2.85 0.79 .12** .08 .21**\\
  {[}.04, .21{]} {[}-.01, .16{]} {[}.13, .29{]}
\item
  onet.challenge.sc 3.66 0.59 .27** .31** .28**\\
  {[}.19, .35{]} {[}.24, .39{]} {[}.20, .35{]}
\end{enumerate}

4 5 6 7 8 9

.60**\\
{[}.54, .65{]}

.18** .37**\\
{[}.10, .26{]} {[}.29, .43{]}

.45** .48** .37**\\
{[}.38, .51{]} {[}.42, .55{]} {[}.30, .44{]}

-.24** -.18** -.02 -.08\\
{[}-.32, -.16{]} {[}-.26, -.09{]} {[}-.10, .06{]} {[}-.16, .00{]}

-.22** -.15** .05 -.07 .86**\\
{[}-.29, -.14{]} {[}-.23, -.07{]} {[}-.03, .13{]} {[}-.16, .01{]} {[}.84, .88{]}

-.22** -.06 -.02 -.12** .66** .69**\\
{[}-.30, -.14{]} {[}-.15, .02{]} {[}-.11, .06{]} {[}-.20, -.04{]} {[}.61, .70{]} {[}.65, .73{]}

-.29** -.18** -.01 -.10* .79** .86**\\
{[}-.37, -.22{]} {[}-.26, -.10{]} {[}-.09, .08{]} {[}-.18, -.02{]} {[}.75, .82{]} {[}.84, .88{]}

-.24** -.25** -.06 -.11** .79** .80**\\
{[}-.32, -.16{]} {[}-.32, -.17{]} {[}-.14, .03{]} {[}-.19, -.03{]} {[}.75, .82{]} {[}.77, .83{]}

-.11** -.10* -.16** -.13** .38** .33**\\
{[}-.19, -.03{]} {[}-.18, -.02{]} {[}-.24, -.08{]} {[}-.21, -.05{]} {[}.31, .45{]} {[}.25, .40{]}

-.19** -.13** -.09* -.23** .62** .62**\\
{[}-.27, -.11{]} {[}-.21, -.04{]} {[}-.17, -.00{]} {[}-.31, -.15{]} {[}.56, .67{]} {[}.56, .66{]}

.41** .33** .08 .33** -.27** -.22**\\
{[}.33, .47{]} {[}.26, .41{]} {[}-.01, .16{]} {[}.25, .40{]} {[}-.34, -.19{]} {[}-.30, -.14{]}

.50** .41** .09* .38** -.26** -.27**\\
{[}.43, .56{]} {[}.34, .48{]} {[}.01, .17{]} {[}.30, .44{]} {[}-.33, -.18{]} {[}-.35, -.19{]}

.34** .30** .29** .38** -.10* -.10*\\
{[}.27, .41{]} {[}.22, .37{]} {[}.21, .36{]} {[}.31, .45{]} {[}-.19, -.02{]} {[}-.18, -.01{]}

.65** .48** .13** .40** -.19** -.18**\\
{[}.60, .70{]} {[}.42, .54{]} {[}.05, .21{]} {[}.33, .47{]} {[}-.27, -.11{]} {[}-.26, -.10{]}

.48** .63** .23** .39** -.16** -.15**\\
{[}.41, .54{]} {[}.58, .68{]} {[}.15, .30{]} {[}.32, .46{]} {[}-.24, -.07{]} {[}-.23, -.07{]}

.13** .26** .66** .29** .06 .12**\\
{[}.05, .21{]} {[}.18, .33{]} {[}.61, .71{]} {[}.21, .36{]} {[}-.03, .14{]} {[}.04, .21{]}

.38** .40** .27** .62** -.10* -.06\\
{[}.31, .45{]} {[}.33, .47{]} {[}.19, .34{]} {[}.56, .66{]} {[}-.18, -.02{]} {[}-.14, .03{]}

10 11 12 13 14 15

.69**\\
{[}.65, .73{]}

.61** .82**\\
{[}.56, .66{]} {[}.80, .85{]}

.47** .35** .47**\\
{[}.41, .54{]} {[}.28, .42{]} {[}.40, .53{]}

.56** .64** .66** .45**\\
{[}.50, .61{]} {[}.58, .68{]} {[}.61, .71{]} {[}.39, .52{]}

-.14** -.21** -.19** -.03 -.12**\\
{[}-.22, -.05{]} {[}-.29, -.13{]} {[}-.27, -.10{]} {[}-.11, .06{]} {[}-.20, -.04{]}

-.21** -.25** -.21** -.04 -.10* .65**\\
{[}-.29, -.13{]} {[}-.33, -.17{]} {[}-.29, -.13{]} {[}-.13, .04{]} {[}-.19, -.02{]} {[}.59, .69{]}

-.23** -.10* -.08* -.06 -.05 .45**\\
{[}-.31, -.15{]} {[}-.18, -.02{]} {[}-.17, -.00{]} {[}-.14, .02{]} {[}-.14, .03{]} {[}.38, .51{]}

-.15** -.27** -.20** -.08* -.16** .50**\\
{[}-.23, -.06{]} {[}-.34, -.19{]} {[}-.28, -.12{]} {[}-.16, -.00{]} {[}-.24, -.08{]} {[}.44, .56{]}

-.09* -.19** -.23** -.10* -.12** .46**\\
{[}-.17, -.01{]} {[}-.27, -.11{]} {[}-.31, -.15{]} {[}-.18, -.02{]} {[}-.20, -.03{]} {[}.39, .52{]}

.05 .07 .04 -.04 -.01 .14**\\
{[}-.03, .14{]} {[}-.01, .15{]} {[}-.05, .12{]} {[}-.12, .04{]} {[}-.09, .07{]} {[}.06, .22{]}

-.10* -.10* -.12** -.13** -.17** .36**\\
{[}-.18, -.02{]} {[}-.18, -.01{]} {[}-.20, -.04{]} {[}-.21, -.05{]} {[}-.25, -.09{]} {[}.29, .43{]}

16 17 18 19 20

.49**\\
{[}.42, .55{]}

.68** .43**\\
{[}.63, .72{]} {[}.36, .49{]}

.60** .39** .70**\\
{[}.54, .65{]} {[}.31, .45{]} {[}.65, .74{]}

.12** .33** .20** .31**\\
{[}.03, .20{]} {[}.25, .40{]} {[}.12, .28{]} {[}.24, .38{]}

.41** .38** .51** .45** .40**\\
{[}.34, .48{]} {[}.30, .45{]} {[}.45, .57{]} {[}.38, .51{]} {[}.33, .46{]}

Note. M and SD are used to represent mean and standard deviation, respectively.
Values in square brackets indicate the 95\% confidence interval.
The confidence interval is a plausible range of population correlations
that could have caused the sample correlation (Cumming, 2014).
* indicates p \textless{} .05. ** indicates p \textless{} .01.
